---
title: "scz"
author: "Line and Solvej"
date: "9 nov 2018"
output: pdf_document
---

# Libraries
```{r}
# libraries 
library(pacman)
p_load(qgraph, bootnet, NetworkComparisonTest,readxl,dplyr,pastecs,smacof,igraph,ggplot2,devtools,gdata)

```

# Read data
```{r}
# Working directory
setwd("C:/Users/Bruger/Google Drev/Cognitive Science/Bachelor/Data")

Scz <- read_excel("Schizophrenia.xlsx")

```

# Topological overlap, clean and subset
```{r}

allScz <- Scz[,c(1:6,14,19,23,28,35,48,53,62,63:68,75,76)]

# col names
colnames(allScz) <- c("Study","ID","Gender","Diagnosis","Age","Education","Affective Flattening","Alogia","Avolition-Apathy","Anhedonia-Asociality","Hallucinations","Delusions","Bizarre Behaviour","Formal Thought Disorder","Verbal Memory","Working Memory", "Motor Function", "Verbal Fluency","Processing Speed", "Executive Functioning", "Triangles Intentionality", "Triangles Appropriatness")

# clean for NA
allScz[allScz == 99] <- NA
allScz <- na.omit(allScz)

# find columns with lilttle or no variation and omit
colSums(allScz != 0)
## --> non

# Subsets

sczFullScz <- dplyr::filter(allScz, allScz$Diagnosis == "Schizophrenia")
sczFullScz <- sczFullScz[,7:22]

sczSymScz <- sczFullScz[,1:8]
colSums(sczSymScz != 0)

sczCogScz <- sczFullScz[,9:16]

sczCogCon <- dplyr::filter(allScz,allScz$Diagnosis=="Control")
sczCogCon <- sczCogCon[,15:22]


```

# Participant descriptives 
```{r}

# participant information Schizophrenia
summary(allScz$Diagnosis)
stat.desc(allScz$Age[allScz$Diagnosis=="Control"])
stat.desc(allScz$Age[allScz$Diagnosis=="Schizophrenia"])
summary(allScz$Gender[allScz$Diagnosis=="Control"])
summary(allScz$Gender[allScz$Diagnosis=="Schizophrenia"])
stat.desc(allScz$Education[allScz$Diagnosis=="Control"])
stat.desc(allScz$Education[allScz$Diagnosis=="Schizophrenia"])

```

# check for normality and density distributions
```{r}

var = c(sczFullScz$`Affective Flattening`,sczFullScz$Alogia,sczFullScz$`Avolition-Apathy`,sczFullScz$`Anhedonia-Asociality`,sczFullScz$Hallucinations,sczFullScz$Delusions,sczFullScz$`Bizarre Behaviour`,sczFullScz$`Formal Thought Disorder`,sczFullScz$`Verbal Memory`,sczFullScz$`Working Memory`,sczFullScz$`Motor Function`,sczFullScz$`Verbal Fluency`,sczFullScz$`Processing Speed`,sczFullScz$`Executive Functioning`,sczFullScz$`Triangles Intentionality`,sczFullScz$`Triangles Appropriatness`)

names = c("Affective Flattening","Alogia","Avolition-Apathy","Anhedonia-Asociality","Hallucinations","Delusions","Bizarre Behaviour","Formal Thought Disorder","Verbal Memory","Working Memory","Motor Function","Verbal Fluency","Processing Speed","Executive Functioning","Triangles Intentionality","Triangles Appropriatness")

dens = c()
qqplot = c()
sharpiro = c()
 
for (i in names){
  d = plot(density(sczFullScz[[i]]))
  dens[[i]]=d
  q = qqnorm(sczFullScz[[i]]);qqline(sczFullScz[[i]])
  qqplot[[i]]=q
  s = shapiro.test(sczFullScz[[i]])
  sharpiro[[i]]=s
  scatter.smooth(sczFullScz[[i]])
}

cog = c("Verbal Memory","Working Memory","Motor Function","Verbal Fluency","Processing Speed","Executive Functioning","Triangles Intentionality","Triangles Appropriatness")

for (i in cog){
plot(density(sczCogCon[[i]]), col = 'deepskyblue', main="",xlab = "",ylab = "")
lines(density(sczCogScz[[i]]), add=T, col = 'deeppink',main="",xlab = "",ylab = "")
title(main=i, sub = "control: blue
      scizophrenics: pink")
}


```


# SczCogScz
```{r}

# estimate networks with different tuning 
set.seed(100)
sczCogScz_net1 <- estimateNetwork(sczCogScz, default = "EBICglasso", tuning = 0.10, corMethod = "cor_auto")
sczCogScz_net2 <- estimateNetwork(sczCogScz, default = "EBICglasso",tuning = 0.25, corMethod = "cor_auto")
sczCogScz_net3 <- estimateNetwork(sczCogScz, default = "EBICglasso",tuning = 0.50, corMethod = "cor_auto")

# number of nodes, edges and mean weight 
summary(sczCogScz_net1)
summary(sczCogScz_net2)
summary(sczCogScz_net3)

# choose network 
sczCogScz_net <- sczCogScz_net2

# plot network spring
png("sczCogScz_spring.png")
sczCogScz_spring <- plot(sczCogScz_net3, layout = "spring", labels = TRUE, nodeNames=sczCogScz_net$labels)
dev.off()

## plot network MDS
    
   #conform to dissimilarity matrix and mds format
sczCogScz_dis <- sim2diss(sczCogScz_net$graph)

sczCogScz_mds <- mds(sczCogScz_dis)
head(round(sczCogScz_mds$conf,2))

   #best fit for transformation 
sczCogScz_ordinal <- mds(sczCogScz_dis,type="ordinal")
plot(sczCogScz_ordinal,plot.type="Shepard",main="Ordinal")
text(0.9,0.2,paste("Stress=",round(sczCogScz_ordinal$stress,2)))

sczCogScz_ratio <- mds(sczCogScz_dis,type="ratio")
plot(sczCogScz_ratio,plot.type="Shepard",main="Ratio")
text(0.9,0.2,paste("Stress=",round(sczCogScz_ratio$stress,2)))

sczCogScz_interval <- mds(sczCogScz_dis,type="interval")
plot(sczCogScz_interval,plot.type="Shepard",main="Interval")
text(0.9,0.2,paste("Stress=",round(sczCogScz_interval$stress,2)))

sczCogScz_mspline <- mds(sczCogScz_dis,type="mspline")
plot(sczCogScz_mspline,plot.type="Shepard",main="Spline")
text(0.9,0.2,paste("Stress=",round(sczCogScz_mspline$stress,2)))
   # --> ORDINAL IT IS

png("sczCogScz_mds.png")

plot(sczCogScz_net, layout = sczCogScz_ordinal$conf, labels = TRUE, nodeNames=sczCogScz_net$labels,color="lightblue",border.color=c("red","red","black","red","red","black","black","black"),border.width=c(4,4,2,4,4,2,2,2),vsize=c(6,8),title="Cognitive Patient Network",title.cex=1.3)
text(-1,-1,paste("Stress=",round(sczCogScz_ordinal$stress,2)))

dev.off()

# nodes are scaled accroding to degree. nodes of interest are highlighted

```

# SczCogScz descriptives 
```{r}

## Global descriptives of the network
   
   # number of nodes, edges and mean weight
summary(sczCogScz_net)

   # conversion to Igraph
sczCogScz_graph <- sczCogScz_net$graph
sczCogScz_Igraph <- graph_from_adjacency_matrix(sczCogScz_graph, weighted=T, mode="undirected", diag=F)
sczCogScz_Igraph_abs <- graph_from_adjacency_matrix(abs(sczCogScz_graph), weighted=T, mode="undirected", diag=F)

   # transitivity: clustering from 0 to 1. measure of redundancy. transitivity takes account of weights
transitivity(sczCogScz_Igraph,"global")
transitivity(sczCogScz_Igraph,"local")
transitivity(sczCogScz_Igraph,"average")

   # path lengths 
shortest.paths(sczCogScz_Igraph_abs)   
average.path.length(sczCogScz_Igraph)
graph.density(sczCogScz_Igraph)
diameter(sczCogScz_Igraph_abs)

   # smallworldness
set.seed(100)
smallworldness(sczCogScz_net)

## Centrality measures 
sczCogScz_cent <- centrality_auto(sczCogScz_net)

png("CogScz_centplot.png")
CogScz_centplot <- centralityPlot(sczCogScz_net)
dev.off()

View(sczCogScz_cent$node.centrality)
write.csv(sczCogScz_cent$node.centrality, file = "CogScz_centtable.txt")

# clustering coefficients
sczCogScz_clust <- clustcoef_auto(sczCogScz_net)
sczCogScz_clust <- round(sczCogScz_clust,digits=2)
write.csv(sczCogScz_clust, file = "sczCogScz_clust.txt")

png("CogScz_clustplot.png")
CogScz_clustplot <- clusteringPlot(sczCogScz_net,signed=TRUE, include = "WS")
dev.off()

#Stability: bootstrap method on complete data, sample 2500 times
boot1_sczCogScz <- bootnet(sczCogScz_net,nBoots = 2500, ncores = 4)

   # Sample and Target lines with CI
plot(boot1_sczCogScz, labels=TRUE, order="sample")

   #Differencetest within network 
   ##edges
plot(boot1_sczCogScz,"edge",plot="difference", onlyNonZero = TRUE, order = "sample")

   ##centrality
plot(boot1_sczCogScz,"strength")
plot(boot1_sczCogScz,"betweenness")
plot(boot1_sczCogScz,"closeness")

# Degree distribution 
result2 <- c()
result <- c()
for (k in 1:100){
  bo <- boot1_sczCogScz$boots
  bo1 <- bo[[k]]
  g_bo1 <- bo1$graph
  for (i in 1:8){
    ab <- abs(g_bo1[i,])
    de <-  sum(ab)
    result[i] <- de
  }
x = result
result2 = c(result2,x)
}

qplot(result2,geom="histogram",binwidth = 0.1, main="Degree distribution", xlab = "weight of edges",ylab="Frequency",fill=..count..,col=I("black"),alpha=I(0.2))
##

#Stability: bootstrap method with case dropping 
boot2_sczCogScz <- bootnet(sczCogScz_net,nBoots = 2500, type = "case", nCores = 4)

plot(boot2_sczCogScz)

corStability(boot2_sczCogScz)


```


# SczCogCon
```{r}
# network estimation using different tunings
set.seed(100)
sczCogCon_net1 <- estimateNetwork(sczCogCon, default = "EBICglasso",tuning = 0.10, corMethod = "cor_auto")
sczCogCon_net2 <- estimateNetwork(sczCogCon, default = "EBICglasso",tuning = 0.25, corMethod = "cor_auto")
sczCogCon_net3 <- estimateNetwork(sczCogCon, default = "EBICglasso",tuning = 0.50, corMethod = "cor_auto")

summary(sczCogCon_net1)
summary(sczCogCon_net2)
summary(sczCogCon_net3)

# choose network
sczCogCon_net <- sczCogCon_net2

# plot network
png("CogCon_spring.png")
CogCon_spring <- plot(sczCogCon_net, layout = "spring", labels = TRUE,nodeNames = sczCogCon_net$labels)
dev.off()

# plot network MDS
##conform to dissimilarity matrix and mds format
sczCogCon_dis <- sim2diss(sczCogCon_net$graph)

sczCogCon_mds <- mds(sczCogCon_dis)
head(round(sczCogCon_mds$conf,2))

##best fit for transformation 
sczCogCon_ordinal <- mds(sczCogCon_dis,type="ordinal")
plot(sczCogCon_ordinal,plot.type="Shepard",main="Ordinal")
text(0.9,0.2,paste("Stress=",round(sczCogCon_ordinal$stress,2)))

sczCogCon_ratio <- mds(sczCogCon_dis,type="ratio")
plot(sczCogCon_ratio,plot.type="Shepard",main="Ratio")
text(0.9,0.2,paste("Stress=",round(sczCogCon_ratio$stress,2)))

sczCogCon_interval <- mds(sczCogCon_dis,type="interval")
plot(sczCogCon_interval,plot.type="Shepard",main="Interval")
text(0.9,0.2,paste("Stress=",round(sczCogCon_interval$stress,2)))

sczCogCon_mspline <- mds(sczCogCon_dis,type="mspline")
plot(sczCogCon_mspline,plot.type="Shepard",main="Spline")
text(0.9,0.2,paste("Stress=",round(sczCogCon_mspline$stress,2)))
# --> ORDINAL IT IS

png("CogCon_mds.png")
CogCon_mds <- plot(sczCogCon_net, layout = sczCogCon_ordinal$conf, labels = TRUE, nodeNames=sczCogCon_net$labels,color="honeydew3",border.color=c("red","red","black","red","red","black","black","black"),border.width=c(4,4,2,4,4,2,2,2),vsize=c(6,8),title="Cognitive Control Network",title.cex=1.3)
text(-1,-1,paste("Stress=",round(sczCogCon_ordinal$stress,2)))
dev.off()


```

# SczCogCon descriptives
```{r}

# Global descriptives

   # conversion to Igraph
sczCogCon_graph <- sczCogCon_net$graph
sczCogCon_Igraph <- graph_from_adjacency_matrix(sczCogCon_graph, weighted=T, mode="undirected", diag=F)
sczCogCon_Igraph_abs <- graph_from_adjacency_matrix(abs(sczCogCon_graph), weighted=T, mode="undirected", diag=F)

   # transitivity: clustering from 0 to 1. measure of redundancy. transitivity takes account of weights
transitivity(sczCogCon_Igraph,"global")
transitivity(sczCogCon_Igraph,"local")
transitivity(sczCogCon_Igraph,"average")

   # path lengths 
shortest.paths(sczCogCon_Igraph_abs)
average.path.length(sczCogCon_Igraph)
graph.density(sczCogCon_Igraph)
diameter(sczCogCon_Igraph_abs)

   # smallworldness
set.seed(100)
smallworldness(sczCogCon_net)

## Centrality measures 
sczCogCon_cent <- centrality_auto(sczCogCon_net)
View(sczCogScz_cent$node.centrality)

png("CogCon_centplot.png")
CogCon_centplot <- centralityPlot(sczCogCon_net)
dev.off()

# clustering coefficients
sczCogCon_clust <- clustcoef_auto(sczCogCon_net)
write.csv(sczCogCon_clust,file="CogCon_clust.csv")
View(sczCogCon_clust)

png("CogCon_clustplot.png")
CogCon_clustplot <- clusteringPlot(sczCogCon_net,signed=TRUE, include = "WS")
dev.off()


#Stability: bootstrap method on complete data, sample 2500 times
boot1_sczCogCon <- bootnet(sczCogCon_net,nBoots = 2500, ncores = 4)

     # Sample and Target lines with CI
plot(boot1_sczCogCon, labels=TRUE, order="sample")

  ##Differencetest within network 

     #edges
plot(boot1_sczCogCon,"edge",plot="difference", onlyNonZero = TRUE, order = "sample")

     #centrality
plot(boot1_sczCogCon,"strength")
plot(boot1_sczCogCon,"betweenness")
plot(boot1_sczCogCon,"closeness")

# Degree distribution 
result2 <- c()
result <- c()
for (k in 1:100){
  bo <- boot1_sczCogCon$boots
  bo1 <- bo[[k]]
  g_bo1 <- bo1$graph
  for (i in 1:8){
    ab <- abs(g_bo1[i,])
    de <-  sum(ab)
    result[i] <- de
  }
x = result
result2 = c(result2,x)
}

qplot(result2,geom="histogram",binwidth = 0.1, main="Degree distribution", xlab = "weight of edges",ylab="Frequency",fill=..count..,col=I("black"),alpha=I(0.2))
##

#Stability: bootstrap method with case dropping 
boot2_sczCogCon <- bootnet(sczCogCon_net,nBoots = 2500, type = "case", nCores = 4)

plot(boot2_sczCogCon)

corStability(boot2_sczCogCon, cor= 0.7)


```


# Comparison controls and patients 
```{r}

# Network Comparison Test (100 itterations)
res <- NCT(sczCogScz,sczCogCon, it = 100, test.edges = TRUE, edges = "all", progressbar = FALSE, gamma = 0.25, paired = FALSE)

# global strength for each network 
res$glstrinv.sep

# difference in global strength 
res$glstrinv.real

# p-value for difference test 
res$glstrinv.pval

# biggest edge difference across networks 
res$nwinv.real

# difference in specific edge weights 
res1 <- res$einv.real
View(res1)

#plot difference network 
qgraph(res1, layout = "spring")

# p-values for difference in specific edge weights 
res1_p <- res$einv.pvals
View(res1_p)

# plot (from itterations) maximum edge difference
plot(res, what="network")

# plot of global strength difference
plot(res, what="strength")

# plot of difference in edge(5,6)
res2 <- NCT(sczCogScz,sczCogCon, it = 100, test.edges = TRUE, edges = list(c(5,6)), progressbar = FALSE, gamma = 0.25, paired = FALSE)
plot(res2, what = "edge")

# spearman correlations
x <- sczCogScz_cent$node.centrality
y <- sczCogCon_cent$node.centrality

cor.test(x$Strength,y$Strength, method = "spearman")
cor.test(x$Betweenness,y$Betweenness, method = "spearman")
cor.test(x$Closeness,y$Closeness, method = "spearman")

# CI edges - overlap check 
b1 <- summary(boot1_sczCogScz)
b2 <- filter(b1,type=="edge")
b3 <- b2[,c(2,6,8,9)]

c1 <- summary(boot1_sczCogCon)
c2 <- filter(c1,type=="edge")
c3 <- c2[,c(2,6,8,9)]

d1 <- rbind(b3,c3)
d1$group <- factor(c(
  rep("Scz",28),
  rep("Con",28)
))

ggplot(d1,aes(x=id,y=mean, colour=group))+
  geom_point()+
  geom_errorbar(aes(ymax=CIupper,ymin=CIlower))+
  coord_flip()

# CI centrality - overlap

b4 <- filter(b1,type=="strength")
b5 <- b4[,c(2,6,8,9)]

c4 <- filter(c1,type=="strength")
c5 <- c4[,c(2,6,8,9)]

d2 <- rbind(b5,c5)
d2$group <- factor(c(
  rep("Scz",8),
  rep("Con",8)
))

ggplot(d2,aes(x=id,y=mean, colour=group))+
  geom_point()+
  geom_errorbar(aes(ymax=CIupper,ymin=CIlower))+
  coord_flip()


```


# SczSymScz
```{r}

# estimate network with different tunings
set.seed(100)
sczSymScz_net1 <- estimateNetwork(sczSymScz, default = "EBICglasso",tuning = 0.1, corMethod = "cor_auto")
sczSymScz_net2 <- estimateNetwork(sczSymScz, default = "EBICglasso",tuning = 0.25, corMethod = "cor_auto")
sczSymScz_net3 <- estimateNetwork(sczSymScz, default = "EBICglasso",tuning = 0.5, corMethod = "cor_auto")

summary(sczSymScz_net1)
summary(sczSymScz_net2)
summary(sczSymScz_net3)

# choose network
sczSymScz_net <- sczSymScz_net3

# plot network
groups_SymScz <- factor(c(
rep("Negative",4),
rep("Positive",4)
))

names_symscz <- c("Affective Flattening","Alogia","Avolition-Apathy","Anhedonia-Asociality","Hallucinations","Delusions","Bizarre Behaviour","Formal Thought Disorder")

png("SymScz_spirng.png")
SymScz_spirng <- plot(sczSymScz_net, layout = "spring", labels = TRUE, nodeNames = names_symscz, groups = groups_SymScz)
dev.off()

# plot network MDS
##conform to dissimilarity matrix and mds format
sczSymScz_dis <- sim2diss(sczSymScz_net$graph)

sczSymScz_mds <- mds(sczSymScz_dis)
head(round(sczSymScz_mds$conf,2))

##best fit for transformation 
sczSymScz_ordinal <- mds(sczSymScz_dis,type="ordinal")
plot(sczSymScz_ordinal,plot.type="Shepard",main="Ordinal")
text(0.9,0.2,paste("Stress=",round(sczSymScz_ordinal$stress,2)))

sczSymScz_ratio <- mds(sczSymScz_dis,type="ratio")
plot(sczSymScz_ratio,plot.type="Shepard",main="Ratio")
text(0.9,0.2,paste("Stress=",round(sczSymScz_ratio$stress,2)))

sczSymScz_interval <- mds(sczSymScz_dis,type="interval")
plot(sczSymScz_interval,plot.type="Shepard",main="Interval")
text(0.9,0.2,paste("Stress=",round(sczSymScz_interval$stress,2)))

sczSymScz_mspline <- mds(sczSymScz_dis,type="mspline")
plot(sczSymScz_mspline,plot.type="Shepard",main="Spline")
text(0.9,0.2,paste("Stress=",round(sczSymScz_mspline$stress,2)))
# --> ORDINAL IT IS

col.sym <- c("orange2","mediumseagreen")

png("SymScz_mds.png")
SymScz_mds <- plot(sczSymScz_net, layout = sczSymScz_ordinal$conf, labels = TRUE, nodeNames=names_symscz,groups = groups_SymScz,color=col.sym, vsize=c(6,8), layoutScale = c(0.8,0.8),legend.cex=0.5,title="Symptom Network",title.cex=1.3)
text(-1,-1,paste("Stress=",round(sczSymScz_ordinal$stress,2)))
dev.off()



```

# SczSymScz descriptives
```{r}

## Global Descriptives 
   
  # conversion to Igraph
sczSymScz_graph <- sczSymScz_net$graph
sczSymScz_Igraph <- graph_from_adjacency_matrix(sczSymScz_graph, weighted=T, mode="undirected", diag=F)
sczSymScz_Igraph_abs <- graph_from_adjacency_matrix(abs(sczSymScz_graph), weighted=T, mode="undirected", diag=F)

   # transitivity: clustering from 0 to 1. measure of redundancy. transitivity takes account of weights
transitivity(sczSymScz_Igraph,"global")
transitivity(sczSymScz_Igraph,"local")
transitivity(sczSymScz_Igraph,"average")

   # path lengths 
shortest.paths(sczSymScz_Igraph_abs)   
average.path.length(sczSymScz_Igraph)
graph.density(sczSymScz_Igraph)
diameter(sczSymScz_Igraph_abs) 

   # smallworldness
set.seed(100)
smallworldness(sczSymScz_net)

## Centrality measures 
sczSymScz_cent <- centrality_auto(sczSymScz_net)
View(sczSymScz_cent$node.centrality)

png("SymScz_centplot.png")
SymScz_centplot <- centralityPlot(sczSymScz_net)
dev.off()

# clustering coefficients
sczSymScz_clust <- clustcoef_auto(sczSymScz_net)
sczSymScz_clust <- round(sczSymScz_clust,digits=2)
View(sczSymScz_clust)
write.csv(sczSymScz_clust,file = "SymScz_clust.csv")

png("SymScz_clustplot.png")
SymScz_clustplot <- clusteringPlot(sczSymScz_net,signed=TRUE, include = "WS")
dev.off()


#Stability: bootstrap method on complete data, sample 2500 times
boot1_sczSymScz <- bootnet(sczSymScz_net,nBoots = 2500, ncores = 4)

plot(boot1_sczSymScz, labels=TRUE, order="sample")

  #Differencetest within network 
      #edges
plot(boot1_sczSymScz,"edge",plot="difference", onlyNonZero = TRUE, order = "sample")

      #centrality
plot(boot1_sczSymScz,"strength")
plot(boot1_sczSymScz,"betweenness")
plot(boot1_sczSymScz,"closeness")

# Degree dist 
result2Sym <- c()
resultSym <- c()
for (k in 1:100){
  bo <- boot1_sczSymScz$boots
  bo1 <- bo[[k]]
  g_bo1 <- bo1$graph
  for (i in 1:8){
    ab <- abs(g_bo1[i,])
    de <-  sum(ab)
    resultSym[i] <- de
  }
x = resultSym
result2Sym = c(result2Sym,x)
}

qplot(result2Sym,geom="histogram",binwidth = 0.1, main="Degree distribution", xlab = "weight of edges",ylab="Frequency",fill=..count..,col=I("black"),alpha=I(0.2))
###


#Stability: bootstrap method with case dropping 
boot2_sczSymScz <- bootnet(sczSymScz_net,nBoots = 2500, type = "case", nCores = 4)

plot(boot2_sczSymScz)

corStability(boot2_sczSymScz)

```


# SczFullScz
```{r}

# estimate network with different tunings
set.seed(100)
sczFullScz_net1 <- estimateNetwork(sczFullScz, default = "EBICglasso",tuning = 0.1, corMethod = "cor_auto")
sczFullScz_net2 <- estimateNetwork(sczFullScz, default = "EBICglasso",tuning = 0.25, corMethod = "cor_auto")
sczFullScz_net3 <- estimateNetwork(sczFullScz, default = "EBICglasso",tuning =  0.5, corMethod = "cor_auto")

summary(sczFullScz_net1)
summary(sczFullScz_net2)
summary(sczFullScz_net3)

# choose network
sczFullScz_net <- sczFullScz_net2

# plot network
groups_fullscz <- factor(c(
rep("Negative Symptoms",4),
rep("Positive Symptoms",4),
rep("Cognitive Measures",8)
))

names_fullscz <- c("Affective Flattening","Alogia","Avolition-Apathy","Anhedonia-Asociality","Hallucinations","Delusions","Bizarre Behaviour","Formal Thought Disorder","Verbal Memory","Working Memory", "Motor Function", "Verbal Fluency","Processing Speed", "Executive Functioning", "Triangles Intentionality", "Triangles Appropriatness")

png("FullScz_spring.png")
FullScz_spring <- plot(sczFullScz_net, layout = "spring", labels = TRUE, nodeNames=names_fullscz, groups=groups_fullscz)
dev.off()

# plot network MDS
##conform to dissimilarity matrix and mds format
sczFullScz_dis <- sim2diss(sczFullScz_net$graph)

sczFullScz_mds <- mds(sczFullScz_dis)
head(round(sczFullScz_mds$conf,2))

##best fit for transformation 
sczFullScz_ordinal <- mds(sczFullScz_dis,type="ordinal")
plot(sczFullScz_ordinal,plot.type="Shepard",main="Ordinal")
text(0.9,0.2,paste("Stress=",round(sczFullScz_ordinal$stress,2)))

sczFullScz_ratio <- mds(sczFullScz_dis,type="ratio")
plot(sczFullScz_ratio,plot.type="Shepard",main="Ratio")
text(0.9,0.2,paste("Stress=",round(sczFullScz_ratio$stress,2)))

sczFullScz_interval <- mds(sczFullScz_dis,type="interval")
plot(sczFullScz_interval,plot.type="Shepard",main="Interval")
text(0.9,0.2,paste("Stress=",round(sczFullScz_interval$stress,2)))

sczFullScz_mspline <- mds(sczFullScz_dis,type="mspline")
plot(sczFullScz_mspline,plot.type="Shepard",main="Spline")
text(0.9,0.2,paste("Stress=",round(sczFullScz_mspline$stress,2)))
# --> ORDINAL IT IS

col.full <- c("lightblue","orange2","mediumseagreen")

png("FullScz_mds.png")
FullScz_mds <- plot(sczFullScz_net, layout = sczFullScz_ordinal$conf, labels = TRUE, nodeNames=names_fullscz,groups = groups_fullscz, color= col.full, vsize=c(6,8), layoutScale = c(1,1),legend.cex=0.4,title="Full Network",title.cex=1.3)
text(-1,-1,paste("Stress=",round(sczFullScz_ordinal$stress,2)))
dev.off()

```

# SczFullScz descriptives
```{r}
## Global descriptives of the network

   # conversion to Igraph
sczFullScz_graph <- sczFullScz_net$graph
sczFullScz_Igraph <- graph_from_adjacency_matrix(sczFullScz_graph, weighted=T, mode="undirected", diag=F)
sczFullScz_Igraph_abs <- graph_from_adjacency_matrix(abs(sczFullScz_graph), weighted=T, mode="undirected", diag=F)

   # transitivity: clustering from 0 to 1. measure of redundancy. transitivity takes account of weights
transitivity(sczFullScz_Igraph,"global")
transitivity(sczFullScz_Igraph,"local")
transitivity(sczFullScz_Igraph,"average")

   # path lengths 
shortest.paths(sczFullScz_Igraph_abs)   
average.path.length(sczFullScz_Igraph)
graph.density(sczFullScz_Igraph)
diameter(sczFullScz_Igraph_abs)

  # smallworldness
set.seed(100)
smallworldness(sczFullScz_net)

# Centrality measures 
sczFullScz_cent <- centrality_auto(sczFullScz_net)
sczFullScz_cent2 <- round(sczFullScz_cent$node.centrality,5)
View(sczFullScz_cent2)
write.csv(sczFullScz_cent2,file = "FullScz_cent.csv")

png("FullScz_centplot.png")
FullScz_centplot <- centralityPlot(sczFullScz_net)
dev.off()

# Clustering coefficients
sczFullScz_clust <- clustcoef_auto(sczFullScz_net)
sczFullScz_clust <- round(sczFullScz_clust,2)
View(sczFullScz_clust)
write.csv(sczFullScz_clust, file = "FullScz_clust.csv")

png("FullScz_clustplot.png")
FullScz_clustplot <- clusteringPlot(sczFullScz_net,signed=TRUE, include = "WS")
dev.off()


#Stability: bootstrap method on complete data, sample 2500 times
boot1_sczFullScz <- bootnet(sczFullScz_net,nBoots = 2500, ncores = 4)

plot(boot1_sczFullScz, labels=FALSE, order="sample")

  ##Differencetest within network 
    #edges
plot(boot1_sczFullScz,"edge",plot="difference", onlyNonZero = TRUE, order = "sample")

    #centrality
plot(boot1_sczFullScz,"strength")
plot(boot1_sczFullScz,"betweenness")
plot(boot1_sczFullScz,"closeness")

# Degree dist 
result2Sym <- c()
resultSym <- c()
for (k in 1:100){
  bo <- boot1_sczFullScz$boots
  bo1 <- bo[[k]]
  g_bo1 <- bo1$graph
  for (i in 1:8){
    ab <- abs(g_bo1[i,])
    de <-  sum(ab)
    resultSym[i] <- de
  }
x = resultSym
result2Sym = c(result2Sym,x)
}

qplot(result2Sym,geom="histogram",binwidth = 0.1, main="Degree distribution", xlab = "weight of edges",ylab="Frequency",fill=..count..,col=I("black"),alpha=I(0.2))
###


#Stability: bootstrap method with case dropping 
boot2_sczFullScz <- bootnet(sczFullScz_net,nBoots = 2500, type = "case", nCores = 4)

plot(boot2_sczFullScz)

corStability(boot2_sczFullScz)

```


# Confidence intervals on Symptoms and Full network
```{r}

# CI centrality - overlap SYM
b7 <- summary(boot1_sczSymScz)
b10 <- filter(b7,type=="strength")
b11 <- b10[,c(2,6,8,9)]

ggplot(b11,aes(x=id,y=mean))+
  geom_point()+
  geom_errorbar(aes(ymax=CIupper,ymin=CIlower))+
  coord_flip()

# CI centrality - overlap FULL
b12 <- summary(boot1_sczFullScz)
b13 <- filter(b12,type=="strength")
b14 <- b13[,c(2,6,8,9)]

ggplot(b14,aes(x=id,y=mean))+
  geom_point()+
  geom_errorbar(aes(ymax=CIupper,ymin=CIlower))+
  coord_flip()


```

